Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-10-12 paper/paper.Rmd
manually specify table column width

```{r observations}
observations <- data.table(
  No. = 1:5,
  Observation = c(
    "Robust to daily reporting artefacts",
    "Some ability to forecast future trend changes",
    "Less reactive to apparent observed changes in trend",
    "Sharper forecasts",
    "A tendency towards underprediction"
    "Modelling the reporting process appears to have little impact"
  )
)

@@

assumptions |>
  kable(
  caption = "(\\#tab:assumptions) Assumptions/simplifications based on observations of the relative performance of Forecast Hub ensembles compared to our forecast submissions.", # nolint
  booktabs = TRUE
  ) |>
  kable_styling(full_width = TRUE)
```

>>>>

```{r observations}
observations <- data.table(
  No. = 1:5,
  Observation = c(
    "Robust to daily reporting artefacts",
    "Some ability to forecast future trend changes",
    "Less reactive to apparent observed changes in trend",
    "Sharper forecasts",
    "A tendency towards underprediction",
    "Modelling the reporting process appears to have little impact"
  )
)

@@

assumptions |>
  kable(
  caption = "(\\#tab:assumptions) Assumptions/simplifications based on observations of the relative performance of Forecast Hub ensembles compared to our forecast submissions.", # nolint
  booktabs = TRUE
  ) |>
  kable_styling(full_width = FALSE) |>
  column_spec(1, width = "3in")
```
